Novelty Detection Using Graphical Models for Semantic Room Classification

### 2011-05-17 semantic-nd/article.tex
removed missing refs.

Dora\cite{dora} (CogX: Dora) was used as a base system where to implement the
presented novelty detection system as it already possesses a developed architecture
oriented on dealing with probabilistic and semantic information and performing
reasoning over it.
Implementing novelty detection capabilities on an agent such as Dora, would allow to
to increase reliability and allow the creation of self-extending behaviours.

@@

As Dora moves through the environment its \emph{conceptual layer} builds a structural and
probabilistic representation of the space instantiated as a \emph{graphical model}.
That model connects the sensed properties together with the variables used to model the world.
And allows to perform queries on the probabilities of aspects of the environment.
For example: where is most likely to find a cereal box\cite{exploiting}.

>>>>

Dora (CogX: Dora) was used as a base system where to implement the
presented novelty detection system as it already possesses a developed architecture
oriented on dealing with probabilistic and semantic information and performing
reasoning over it.
Implementing novelty detection capabilities on an agent such as Dora, would allow to
to increase reliability and allow the creation of self-extending behaviours.

@@

As Dora moves through the environment its \emph{conceptual layer} builds a structural and
probabilistic representation of the space instantiated as a \emph{graphical model}.
That model connects the sensed properties together with the variables used to model the world.
And allows to perform queries on the probabilities of aspects of the environment.
For example: where is most likely to find a cereal box.
